An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-28 Revision/response.tex

\noindent
\textbf{Response:} 
Thank you for pointing this out. Both paper [49] and our paper are benchmarks. Paper [49] provides a comprehensive review and evaluation of graph-based approximate nearest neighbor search algorithms. Our paper is the first benchmark to evaluate hybrid queries. Since hybrid queries are developed based on ANN, we refer to the evaluation metrics proposed in the cited paper. We realize that we did not clearly explain the difference between our paper and the cited paper, so we have added a description in the introduction, please see section 1.1.

\textcolor{blue}{"Although existing work, such as the survey [49] by reviews graph-based ANN methods, the literature still lacks an experimental study specifically targeting hybrid query algorithms. To address this gap, we conduct the first comprehensive experimental evaluation of hybrid query algorithms, systematically analyzing their index construction costs and query efficiency across diverse scenarios. Furthermore, we rigorously assess the robustness of each algorithm under varying conditions, thereby providing valuable insights for future research and practical applications."}

%%%%%%%%%%%%%%%%%%%%%% D2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Section 1.1, I could not find convincing references for the requirements in practical applications.
			[12] and [36] are research papers only, but not from real applications.}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thank you for your suggestion. We cited these two papers in the introduction to show that there are several papers that study attribute distribution and selectivity.
In addition, attribute distribution and selectivity are indeed widely used in real-world scenarios. For attribute distribution, the label attributes of many recommendation application scenarios in reality conform to the power-law distribution. For attribute selectivity: For example, if you need to query data with a very small proportion of a certain attribute, choosing a better algorithm will greatly improve the search effect. There are also some databases with practical applications that mention attribute selectivity, such as Milvus and AnalyticDB-V. For the two parts you suggested, we have added more comprehensive references in the paper.

@@

\textbf{Regarding quantization time in index build:}

Of all the evaluated algorithms, Faiss, Puck, DiskANN, and Milvus support quantization. However, in our experiments, we did not enable quantization in any of our experiments. Therefore, no quantization time was included in the reported index build times.

\textbf{Regarding Figure 7 and the exclusion of Vamana:}

We appreciate the observation of reviewer. Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic. The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included. Since other algorithms also do not support multi-attribute queries, we have explained this situation collectively in the corresponding section of the paper to save space. (\textbf{Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.})

### 2025-07-28 VLDB2026/main.tex
1

	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets. By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method. We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios. Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.

@@

%	\subsection{Index Organization in Hybrid ANN Search}
	\subsection{Index Organization in Hybrid Query}

>>>>

	(3)\textbf{ Evaluation of Attribute Filtering Algorithms.}
	%We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. 
%	We systematically evaluate 6 attribute filtering algorithms, 1 library, and 3 databases on 7 real-world datasets. By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method. We further examine their behavior under different attribute distributions and selectivity to assess robustness and adaptability in complex query scenarios. Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
	\textcolor{orange}{We conduct a comprehensive evaluation of 6 attribute filtering algorithms, 1 library, and 3 databases across 6 basic datasets, 2 real-world datasets, one 100M-scale dataset, and 2 multimodal datasets. By analyzing the query performance of each method under various scenarios, we reveal their respective strengths and weaknesses. We further examine their robustness by evaluating performance under different attribute distributions and selectivity levels. To ensure fairness and generality, we evaluate the methods on two different server environments. The evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.}

@@

%	\subsection{Index Organization in Hybrid ANN Search}
	\subsection{Index Organization}
